TGI-spinal-power

### 2022-05-03 analysis/tgispine_lme_power.Rmd
pushing to git
doing the same for warm - model, power & power curve

Now to run a power curve on the data to find out the optimal number of participants needed for the effect of interest
```{r}
# can run a power curve to determine the point of trade off between N observations and power
pc.cold <- powerCurve(model.coldN, within='manipulation+condition+cold_location', 
                      breaks= seq(0, 30, by = 3))
print(pc.cold)
```

# Plot power curve!
```{r}

```

>>>>

Now to run a power curve on the data to find out the optimal number of participants needed for the effect of interest
```{r}
# can run a power curve to determine the point of trade off between N observations and power
pc.cold <- powerCurve(model.coldN, within='manipulation+condition+cold_location', 
                      breaks= seq(1, 30, by = 3))
print(pc.cold)
```

# Plot power curve!
```{r}
plot(pc.cold) # a good visualisation :)
```

Now let's do the same for warm!
# Warm model
```{r}
model.warm <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID),
                   data = df_sum[df_sum$VAS == 'warm' ,])
summary(model.warm)
```

# Extend the model observations to n = 50, and extract smallest effect size of interest
```{r}
# using n050 here as expecting smaller effect sizes
model.warmN <- extend(model.warm, within = 'manipulation+condition+cold_location', n=50)
# extracting effect sizes from the extended model
tgi_effect <- fixef(model.warmN)["manipulationTGI"]
cond_effect <- fixef(model.warmN)["conditionwithin"]
cold_loc_effect <- fixef(model.warmN)["cold_locationprox_caud"]
# add smallest effect size - same as cold model
fixef(model.coldN)["cold_locationprox_caud"] <- cold_loc_effect

# then run power analysis
pwr.warm <- powerSim(model.warmN)
print(pwr.warm)
```
# Run a power curve on these data with n = 50
```{r}
# can run a power curve to determine the point of trade off between N observations and power
pc.warm <- powerCurve(model.warmN, within='manipulation+condition+cold_location', 
                      breaks= seq(1, 50, by = 5))
print(pc.warm)
```
